Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-21 latex_files/applied_network_science_article/article_v0.tex

Let $S_i$ denote the \emph{set of stops which can be reached from stop $i$ outside lines connection} (with, e.g., an acceptable walking distance), excluding $i$ itself. A stop $i$ is referred to as an \emph{isolated stop} if $S_i=\emptyset$, and to as a \emph{junction} otherwise.

@@

First, we shows some algorithm iterations on a toy example with $p=2$, where $100$ passengers where drawn uniformly across the $\vert P \vert = 20$ possible st-trips. Some iterations of the algorithm with $\theta=0.1$, along with MTE and MME errors, are shown in Figure \ref{iteration_plots}. 
\begin{figure}[h]
	\label{iteration_plots}
	\includegraphics[width=0.98\textwidth]{fig/iterations.pdf}
	\caption{Real transportation flow (green arrows) obtained by randomly drawing $100$ passengers on the graph toy example with $p=2$ line tours, along with iterations $1, 3, 6, 10, 15$ of the algorithm with $\theta=0.1$. MTE and MME errors are computed, and embarkment and disembarkment flows are represented respectively by the red and blue colors on nodes.}
\end{figure}
On this small example, we can see that the algorithm quickly find an estimation giving small MME error, but still give an MTE of 0.252. This result is due to the fact that only $100$ passengers are drawn, giving a large deviation compared to the optimally found solution which maximize the entropy. Interestingly, we see that a better result is found on iteration 6, but margins constraints at this point are not perfectly respected yet.

>>>>

Let $S_i$ denotes the \emph{set of stops which can be reached from stop $i$ outside lines connection} (with, e.g., an acceptable walking distance), excluding $i$ itself. A stop $i$ is referred to as an \emph{isolated stop} if $S_i=\emptyset$, and to as a \emph{junction} otherwise.

@@

First, we shows some algorithm iterations on a toy example with $p=2$, where $100$ passengers where drawn uniformly across the $\vert P \vert = 20$ possible $st$-trips. Some iterations of the algorithm with $\theta=0.1$, along with MTE and MME errors, are shown in Figure \ref{iteration_plots}. 
\begin{figure}[h]
	\label{iteration_plots}
	\includegraphics[width=0.98\textwidth]{fig/iterations.pdf}
	\caption{Real transportation flow (green arrows) obtained by randomly drawing $100$ passengers on the graph toy example with $p=2$ line tours, along with iterations $1, 3, 6, 10, 15$ of the algorithm with $\theta=0.1$. MTE and MME errors are computed, and embarkment and disembarkment flows are represented respectively by the red and blue colors on nodes.}
\end{figure}
On this small example, we can see that the algorithm quickly find an estimation giving small MME error, but still give an MTE of 0.252. This result is due to the fact that only $100$ passengers are drawn, giving a large deviation compared to the optimally found solution which maximize the entropy. Interestingly, we see that a better result is found on iteration 6, but margins constraints at this point are not perfectly respected yet.
